THESIS PROJECT PROPOSAL

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter 
particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be 
produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.

@@

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson. Using b-jet tagging algorithms, the ejt originating from b-quark can be reconstructed to identity 
top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks like 
top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly to 
the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the Higgs 
boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. There 
are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which are 
Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
quark with a Higgs boson(tH).

>>>>

The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter 
particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
can be produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.

@@

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
the top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks 
like top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly 
to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the 
Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. 
There are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which 
are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.
